\section{Introduction}

\note{See discussion on common material and timing considerations in \cite{PSTN-020}.}

\note{This outline proceeds assuming this paper is being produced at the end of commissioning/early operations, and some form of routine alert production is happening in operations based on commissioning-derived or incremental templates.

If only a small amount of LSSTCam commissioning data is available and is being released, only a minimal paper decribing the pipelines used to process that data would useful, and a more complete AP reference should come later.}

\note{Information about the processing environment is presumed to be covered in \cite{PSTN-018}.
}

\note{SS Processing falls under Prompt Processing but detailed discussion is deferred to \cite{PSTN-025}.}


\section{Pipeline}
\note{following LDM-151}
\subsection{Single Frame Processing}

\note{Construction of calibration products assumed described in \cite{PSTN-026}.}

ISR, PSF and Background fitting, photometric and astrometric calibration.  Likely major commonalities with DRP.

\subsection{Template Generation}

\note{Pre-DR1 this may require description independent of DRP.}

High-level discussion of DCR correction could go here.

\subsection{Image Differencing}

\subsection{Source Detection}

Including discussion of point source, dipole, and streak detection on difference images.  

\note{Algorithmic basics could be discussed elsewhere}

\subsection{Spuriousness scoring}

Algorithm, training, and performance of the ML spuriousness score

\subsection{AP Source Association}

Algorithms and interface considerations with the PPDB

\note{does \cite{PSTN-045} describe the APDB/PPDB implementation?}

\subsection{Alert Generation}

Formats \& contents

\subsection{Alert Distribution}

Mechanisms, connections to community brokers

\subsection{Alert Filtering Service}

\subsection{Forced Photometry}


\section{Prompt Data Products}


Summary of relevant aspects of the DPDD \citep{LSE-163}, including latency considerations and user access.

\begin{itemize}
  \item Images
  \item Prompt Catalogs and the PPDB
  \item Alerts
\end{itemize}


