
\section{Pipeline}

%\note{following LDM-151}

\subsection{Single Frame Processing}

\note{Construction of calibration products assumed described in \cite{PSTN-026}.}

ISR, PSF and Background fitting, photometric and astrometric calibration.  Likely major commonalities with DRP.

\subsection{Template Generation}

\note{Pre-DR1 this may require description independent of DRP.}

High-level discussion of DCR correction could go here.

\subsection{Image Differencing}

\subsection{Source Detection and Measurement}

Including discussion of point source, dipole, and streak detection on difference images.  

\note{Algorithmic basics could be discussed elsewhere}

\subsection{Reliability scoring}

Image-differencing searches for transients typically contend with high rates of false positives.
Among the raw detections, artifacts may dominate real astrophysical sources by an order of magnitude.
These may be due to imperfectly-corrected instrument signatures, astrometric mismatches between the template and the science image, cosmic rays, or algorithmic failures in the differencing.
Modern surveys employ machine-learned classifiers to winnow these candidates \citep[e.g.,][]{Bailey:07:NearbySNFML,Bloom:12:RealBogus,Brink:13:RB2,Wright:15:PS1ML,Goldstein:15:DESRealBogus,Duev:19:Braii}.
These have steadily improved in performance and sophistication as the classifiers transitioned from Random Forest models trained on manually-constructed feature sets to deep neural networks trained directly on image pixels.
Some approaches have combined both detection and scoring without using the difference image \citep{Sedaghat:17:Transinet,Acero-Cuellar:22:NoDifference}.

\todo{overview of the algorithm, training, and performance of the ML spuriousness score; detailed discussion likely deferred to separate paper}

\subsection{Source Association}

Algorithms and interface considerations with the PPDB

\note{does \cite{PSTN-045} describe the APDB/PPDB implementation?}

\subsection{Alert Generation}

Formats \& contents

\subsection{Alert Distribution}

Mechanisms, connections to community brokers

\subsection{Alert Filtering Service}

\subsection{Forced Photometry}

\subsection{Source Injection}

\subsection{Metrics}